\documentclass[12pt,letterpaper,onecolumn]{report}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{amstext}
\usepackage{amsthm}
\usepackage{graphicx}
\usepackage{exscale}
\usepackage[mathscr]{eucal}
\usepackage{bm}
\usepackage{eqlist}
\usepackage[usenames, dvipsnames]{color}
\DeclareGraphicsExtensions{.pdf, .jpg}
\newcommand{\harpoon}{\overset{\rightharpoonup}}

\usepackage{hyperref}
\usepackage{esint}
\usepackage{mathtools}
\usepackage{colortbl}
\usepackage{color}
\usepackage[utf8]{inputenc}

\usepackage[left=1in,right=1in,top=1in,bottom=1in]{geometry}

\usepackage{enumitem}
\usepackage{fancyhdr}
\pagestyle{fancy}
%\fancyhf{}
\lhead{\textbf{Lab 2}}
\chead{\textbf{ENGR 3230: Analog Circuit Design}}
\rhead{10 pts}


\begin{document}

\begin{center}
\LARGE{\textbf{Lab 2: Test Apparatus Construction}}\\
\Large{Due: Tuesday 02/12/2019}
\\

\end{center}

\section*{Objectives}
\begin{enumerate}
\item To design and construct a test apparatus for guitar pedals for labs in Analog Circuit Design.

\end{enumerate}

\section*{Supplies}
\begin{itemize}
\item Two 1/4 inch audio jacks
\item One breadboard
\item One 3PDT switch
\item One toggle switch
\item Any other materials you can find or make in the engineering center
\end{itemize}

\section*{Requirements}
Build a test apparatus with your lab partner to build and test guitar pedal circuits on.  We will make use of this apparatus regularly throughout the semester.  The requirements are as follows:
\begin{itemize}
\item The apparatus should be self contained and portable.
\item The toggle switch should be mounted, and be wired into the breadboard (solder wires to the terminals and connect them to independent nodes in the breadboard)
\item There should be places to mount potentiometers.  You will be provided one potentiometer so that you can make holes the correct size.
\item  One 1/4 inch audio jack is an input.  It should be mounted.  It should also be possible to inject an input into the circuit using a function generator.
\item One 1/4 inch audio jack is an output.  It should be mounted.  It should also be possible to measure the output signal with an oscilloscope.
\item There should be clear labeling for power and ground rails for circuits built on this apparatus.
\item The apparatus should be wired in true bypass with the 3PDT switch used to turn the circuit on or off.
\end{itemize}

\noindent Submit a short report (one per group) written in \LaTeX\ that includes at a minimum, the following components:
\begin{itemize}
\item A 3D model of your test apparatus (Fusion360)
\item A picture of your test apparatus, showing that it matches the 3D model
\item A short discussion of any design choices made for the apparatus
\end{itemize}

\end{document}
